Review: Crop adaptation through post-domestication introgression from wild relatives

### 2016-05-26 TiG_prospectus.tex
edits to prospectus

\section*{Crop adaptation through introgression}
Over the last few years, several high-profile publications based on genome-wide data have documented introgression between crops and wild relatives outside putative domestication centers. A history of introgression during diffusion appears to be rule for crops rather an exception.
\begin{enumerate}
	\item{Crops, given their frequent history of diffusion from defined centers of origin, are ideal recipients of adaptive introgression. Theory suggests that such colonizing species will overwhelmingly be recipients rather than donors of introgression \cite{Currat2008}.}
	\item{Empirical studies are revealing that introgression has occurred in many of the world's most important crops.}
	\begin{enumerate}
		\item{Maize: As maize spread from a lowland center of origin it received introgression from a highland-adapted wild relative \cite{Hufford2013}}
		\item{Sunflower: \cite{Baute2015}}
		\item{Rice: \cite{Huang2012}}
		\item{Barley: \cite{Poets2015}}
		\item{Olive: \cite{Diez2015}}
		\item{Cassava: \cite{Bredeson2016}}
	\end{enumerate}
\end{enumerate}

>>>>

\section*{Crop adaptation through introgression}
Over the last few years, several high-profile publications based on genome-wide data have documented introgression between crops and wild relatives outside putative domestication centers. A history of introgression during diffusion appears to be rule for crops rather an exception.
\begin{enumerate}
	\item{Crops, given their frequent history of diffusion from defined centers of origin, are ideal recipients of adaptive introgression. Theory suggests that such colonizing species will overwhelmingly be recipients rather than donors of introgression \cite{Currat2008}.}
	\item{Empirical studies are revealing that introgression has occurred in many of the world's most important crops.}
	\begin{enumerate}
		\item{Maize: As maize spread from a lowland center of origin it received introgression from a highland-adapted wild relative \cite{Hufford2013}.}
		\item{Sunflower: Domesticated sunflower has received substantial introgression from wild relatives post-domestication that has potentially reintroduced a branching morphology \cite{Baute2015}.}
		\item{Rice: \cite{Huang2012}}
		\item{Barley: Landraces of barley show shared ancestry with geographically-proximate populations of wild relatives suggesting introgression \cite{Poets2015}.}
		\item{Olive: \cite{Diez2015}}
		\item{Cassava: \cite{Bredeson2016}}
	\end{enumerate}
\end{enumerate}
